NumPy---Array Programming in Python

### 2020-01-11 body.tex
Add text from Sebastian

@@

To address these issues NumPy has the goal of providing the fundamental
API for \emph{interoperability} between the various NumPy-like APIs.
For example, a new array protocol was implemented that allows NumPy to consume
array-like objects produced by libraries outside of NumPy.  When asking NumPy
to, e.g., sum such an array, instead of attempting that operation itself, NumPy
requests the original array to complete the computation.  This means that the
NumPy API---the syntax for interacting with arrays---can still be used, but now
with a library that supports GPUs, does distributed computation processing, or
stores data in the cloud.

@@

The second factor flows from Python's nature as an open-source language,
embedded within the open-source community.  Python attracts developers who like
to build and contribute.  As a result, NumPy has always been a library that was
developed by scientists in order to do their work.  Commercial specialist
numerical languages can encourage consumer-users, who pick up a tool and use
it, but do not expect to contribute to development%<-sentence a bit tough to parse.
In contrast, NumPy often
attracts user-developers, who want to work with NumPy, and are prepared to fix
and extend the library as they work. User-developers have been the fundamental
force in developing NumPy, and shaping it into a library that has been refined
in the furnace of practical scientific work.

>>>>

While NumPy remains the fundamental tool of choice for a large portion
of applications the growth of the computational landscape and methods
cannot be supported within a single library.
However, the NumPy API is a preferred language for array computation
and often one of the first tools learned.

@@

To address these issues NumPy has the goal of providing the fundamental
API for \emph{interoperability} between the various NumPy-like APIs.
We believe that improving the interoperability and moving NumPy forward
to serve new arising needs where possible is the best way to balance
the need for stability on the one hand while supporting the growth of
specialized solutions and new tools on the other.

For example, a new array protocol was implemented that allows NumPy to consume
array-like objects produced by libraries outside of NumPy.  When asking NumPy
to, e.g., sum such an array, instead of attempting that operation itself, NumPy
requests the original array to complete the computation.  This means that the
NumPy API---the syntax for interacting with arrays---can still be used, but now
with a library that supports GPUs, does distributed computation processing, or
stores data in the cloud.

@@

The second factor flows from Python's nature as an open-source language,
embedded within the open-source community.  Python attracts developers who like
to build and contribute.  As a result, NumPy has always been a library that was
developed by scientists in order to do their work.  Commercial specialist
numerical languages can encourage consumer-users, who pick up a tool and use
it, but do not expect to contribute to development. %<-sentence a bit tough to parse.
In contrast, NumPy often
attracts user-developers, who want to work with NumPy, and are prepared to fix
and extend the library as they work. User-developers have been the fundamental
force in developing NumPy, and shaping it into a library that has been refined
in the furnace of practical scientific work.
